Tutorial_2b

### 2024-12-05 Tutorial_2b.Rmd
minor edits 2b.

```{r prepare-data}
# select analysis time range: (200,600]
ca_data <- ca_data %>% filter(drt > 5) %>%

# create factor condition, with "blank" as the reference level
mutate(condition = factor(condition, 
                          labels = c("blank", "congruent","incongruent")),
       prime = ifelse(condition=="blank",1, ifelse(condition=="congruent",2,3)),
      prime = factor(prime,levels=c(1,2,3)),
       timebin = factor(drt, levels=c(6:15)),
       period_9 = drt - 9,
       trial_c = (trial - 1000)/1000)

head(ca_data)
```

>>>>

```{r prepare-data}
# select analysis time range: (200,600]
ca_data <- ca_data %>% 
  filter(drt > 5) %>%
  # create factor condition, with "blank" as the reference level
  mutate(condition = factor(condition, 
                            labels = c("blank", "congruent","incongruent")),
         prime = ifelse(condition=="blank",1, 
                 ifelse(condition=="congruent",2,3)),
         prime = factor(prime,levels=c(1,2,3)),
         timebin = factor(drt, levels=c(6:15)),
         period_9 = drt - 9,
         trial_c = (trial - 1000)/1000) 
head(ca_data)
```
